---
title: "Project_STA518"
author: "Cleyde Murillo, Jr., Nathanial VanDyk"
date: "10/13/2021"
output:
  html_document:
    df_print: paged
---

Setup

```{r setup, message = FALSE}
library(tidyverse)
library(data.table)
library(readr)
library(corrr)
library(infer)
options(scipen = 999)
```

> Loading in Customer data

```{r message = FALSE}
customers <- read_tsv("marketing_campaign.csv")
summary(customers)
```

Variable Dictionary:

`ID` = Customer's Unique Identifier
`Year_Birth` = Customer's birth year
`Education` = Customer's education level
`Marital_Status` = Customer's marital status
`Income` = Customer's yearly household income
`Kidhome` = Number of children in customer's household
`Teenhome:` = Number of teenagers in customer's household
`Dt_Customer` = Date of customer's enrollment with the company
`Recency` = Number of days since customer's last purchase
`Complain` = 1 if customer complained in the last 2 years, 0 otherwise

`MntWines` = Amount spent on wine in last 2 years
`MntFruits` = Amount spent on fruits in last 2 years
`MntMeatProducts` = Amount spent on meat in last 2 years
`MntFishProducts` = Amount spent on fish in last 2 years
`MntSweetProducts` = Amount spent on sweets in last 2 years
`MntGoldProds` = Amount spent on gold in last 2 years

`NumDealsPurchases` = Number of purchases made with a discount
`AcceptedCmp1` = 1 if customer accepted the offer in the 1st campaign, 0 otherwise
`AcceptedCmp2` = 1 if customer accepted the offer in the 2nd campaign, 0 otherwise
`AcceptedCmp3` = 1 if customer accepted the offer in the 3rd campaign, 0 otherwise
`AcceptedCmp4` = 1 if customer accepted the offer in the 4th campaign, 0 otherwise
`AcceptedCmp5` = 1 if customer accepted the offer in the 5th campaign, 0 otherwise
`Response` = 1 if customer accepted the offer in the last campaign, 0 otherwise

`NumWebPurchases` = Number of purchases made through the company’s web site
`NumCatalogPurchases` = Number of purchases made using a catalogue
`NumStorePurchases` = Number of purchases made directly in stores
`NumWebVisitsMonth` = Number of visits to company’s web site in the last month


Exploratory Data Analysis
===========================================

```{r outliers}
outliers <- customers %>% 
        filter(Income > 200000 | is.na(Income))
customers <- customers %>% 
  anti_join(outliers)

```


We will be generating visualizations (density plots, histograms, scatter plots) to understand how the data behaves

```{r Density_Plots}
ggplot(data=customers, aes(x=Income, group=Marital_Status, fill=Marital_Status)) +
    geom_density(adjust=1.5) +
    theme_classic() +
    facet_wrap(~Marital_Status) +
    theme(
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      axis.ticks.x=element_blank()
    )

ggplot(data=customers, aes(x=Income, group=Education, fill=Education)) +
    geom_density(adjust=1.5) +
    theme_classic() +
    facet_wrap(~Education) +
    theme(
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      axis.ticks.x=element_blank()
    )
```

```{r histogram}
p1 <- ggplot(data=customers, aes(customers$Year_Birth)) + 
  geom_histogram(aes(y =..density..), 
                 col="red", 
                 fill="blue", 
                 alpha = .2) + 
  geom_density(col=2) + 
  labs(title="Histogram for Year of Birth") +
  labs(x="Year", y="Count")
p2 <- ggplot(data=customers, aes(customers$Income)) + 
  geom_histogram(aes(y =..density..), 
                 col="red", 
                 fill="blue", 
                 alpha = .2) + 
  geom_density(col=2) + 
  labs(title="Histogram for Income") +
  labs(x="Income", y="Count")

gridExtra::grid.arrange(p1,p2)
```

```{r scatterplots}
ggplot(customers, aes(y=NumStorePurchases, x=Income, color=Marital_Status)) +
  geom_point()
```


```{r correlation}
customer_cor <-customers %>% 
  select(-ID, -Year_Birth, -Marital_Status, -Dt_Customer, -Education) %>% 
  correlate()%>%
  shave()
  
rplot(customer_cor)

```




```{r Bootstrapping}

boot_customers <- customers %>%
  rep_sample_n(size = nrow(customers),
               replace = TRUE,
               reps = 10)


```

```{r Bootstrapping mean}

#boot_customers_mean <- boot_customers %>% 
  #group_by(Income) %>% 
  #summarise(mean_customer = mean(customers))
summary(boot_customers)




```

